---
title: "Quiz 3"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Question 1
For which of the following situations would a 0/1 loss function make the most sense?

Your prediction for the number of bikes sold this year by a local bike shop.  
Your answer choice on a Coursera multiple choice quiz.  
__Your prediction as to whether it will rain tomorrow.__  
Your estimate of the market price of your house.  

### Question 2
Fill in the blank: Under a __linear loss function__, the summary statistic that minimizes the posterior expected loss is the ⎯⎯⎯⎯⎯⎯⎯⎯⎯⎯⎯⎯⎯ of the posterior.

Mode  
Mean  
__Median__

### Question 3
You are employed in the Human Resources department of a company and are asked to predict the number of employees that will quit their jobs in the coming year. Based on a Bayesian analysis of historical data, you determine the posterior predictive distribution of the number of quitters to follow a Poisson($\lambda=10$) distribution. Given a __quadratic__ loss function, what is the prediction that minimizes posterior expected loss?

a. 9  
b. 10  
c. 11  
d. Either a or b  

### Question 4
Suppose that you are trying to decide whether a coin is biased towards heads (p=0.75) or tails (p=0.25). If you decide incorrectly, you incur a loss of 10. Flipping another coin incurs a cost of 1. If your current posterior probability of a head-biased coin is 0.6, should you make the decision now or flip another coin and then decide?

__hypotheses__
H1: heads bias
H2: tails bias

__priors__
p(H1)=0.75
p(H2)=0.25

__decisions__
d1: decide now
d2: flip another coin and then decide

__posteriors__
p(H1|D)=0.6
p(H2|d)=0.4

__losses__
$\begin{aligned}
L(d_1)=
  \left\{
    \begin{array}{l}
      0 \text{ if coin is heads biased }\implies d_1 \text{ is right}\\
      w_1=10\text{ if coin is not heads biased }\implies d_1 \text{ is wrong}
    \end{array}
  \right.
\end{aligned}$

$\begin{aligned}
L(d_2)=
  \left\{
    \begin{array}{l}
      0 \text{ if coin is heads biased }\implies d_1 \text{ is right}\\
      w_1=10\text{ if coin is not heads biased }\implies d_1 \text{ is wrong}
    \end{array}
  \right.
\end{aligned}$

### Question 6
Suppose that you are trying to estimate the true proportion p of male births in the United States. Starting with a strong prior (Beta(500,500)) on the proportion, you randomly sample 10,000 birth certificates, observing 5029 males and 4971 females. What is the posterior probability that p is less than or equal to 0.5? (Hint: use function(s) in R to answer this question)
```{r}
a<-500
b<-500
n<-10000
x<-5029
alpha<-a+x
beta<-b+n-x
pbeta(0.5,alpha,beta)
```






